Notes on generating initial models for mapping into {\tt MAESTRO}

### 2008-08-22 docs/initial_models/paper.tex
instead of averaging model points to get a coarse value, I changed the text to say linearly interpolate between the two closest points.  This is more accurate for problems with 3+ levels
rewrote the fine -> coarse HSE pressure stencil to look more like how the code will be
finished notes on coarse-fine HSE discretizations

\item Copy the initial data from the dots directly into the circles.  For the squares, compute only $\rho$ and $X$ by averaging $\rho$ and $(\rho X)$ from the two corresponding dots.
\item Integrate to get $p$ in the squares.  We need a fancy stencil at coarse-fine interfaces that I haven't finished deriving.  Away from coarse-fine interfaces, we can use our standard HSE discretization.
\item Call EOS to get $T$ and $h$ in the squares, i.e., $T,h = Th,h(\rho,p,X)$.

@@

\subsubsection{Working Notes on Coarse-Fine HSE Discretization - Not Final}

@@

&=& p_{\sfrac{r}{2}-1}^{l-1} + \frac{3\Delta r^l g}{4}\left(\rho_{\sfrac{r}{2}-1}^{l-1} + \rho_r^l\right).

@@

p_{r}^l = p_{2(r-1)+1}^{l+1} + \frac{3\Delta r^{l+1}g}{4}\left(\rho_{2(r-1)+1}^{l+1} + \rho_{r}^l\right).

>>>>

\item Copy the initial data from the dots directly into the circles.  For the squares, compute only $\rho$ and $X$ by using linear interpolation from the two nearest corresponding dots.\MarginPar{Maybe we should use quadratic interpolation?}
\item Integrate to get $p$ in the squares.  We need the fancy stencils at coarse-fine interfaces in equations (\ref{Coarse-Fine Stencil}) and (\ref{Fine-Coarse Stencil}).  Away from coarse-fine interfaces, we can use our standard HSE discretization.
\item Call EOS to get $T$ and $h$ in the squares, i.e., $T,h = T,h(\rho,p,X)$.

@@

\subsubsection{Coarse-Fine HSE Discretization}

@@

&=& p_{\sfrac{r}{2}-1}^{l-1} + \frac{3\Delta r^l g}{4}\left(\rho_{\sfrac{r}{2}-1}^{l-1} + \rho_r^l\right).\label{Coarse-Fine Stencil}

@@

p_{(r+1)/2}^{l-1} = p_{r}^l + \frac{3\Delta r^l g}{4}\left(\rho_{r}^l+\rho_{(r+1)/2}^{l-1}\right).\label{Fine-Coarse Stencil}
